An efficient audio coding scheme for quantitative and qualitative large scale acoustic monitoring using the sensor grid approach

### 2017-11-20 paper/articleV2.tex
anr funding

The authors would like to thank Christophe d'Alessandro for fruitful discussion on speech intelligibility.

>>>>

The authors would like to acknowledge partial funding from the ANR under project reference ANR-16-CE22-0012 and to thank Christophe d'Alessandro for fruitful discussion on speech intelligibility.
